Notebook of learning from ensemble labels

### 2021-07-03 docs/notebook_learn_dl_ensemble.Rmd
Update some details
Add some updates

```
python hrlcm/fit_coteaching_compare.py --exp_name unet_cot_argue --num_workers 32 --gpu_devices '0,1,2,3' --epochs 30
```

>>>>

```
python hrlcm/fit_coteaching.py --exp_name unet_cot_noisy8_40 --lowest_score 8 --num_workers 32 --gpu_devices '0,1,2,3' --num_gradual 10
```

```
python hrlcm/fit_compose_lr.py --exp_name dpl_compose_lr --num_workers 32 --model deeplab --gpu_devices '0,1,2,3' --train_batch_size 16 --val_batch_size 16
```
